### 2023-09-08 main.tex
fixed
Motivation Q0-1

\textbf{Proof of \eqref{BActionVoid}: } using \eqref{B-charge} we have that 
\begin{align}
	B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=&2 \left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}\sum_{k=1}^{N}e_{kN}^{[a]}e_{jk}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber
	\\=&
	2\left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}e_{NN}^{[a]}e_{jN}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber\\=&
	\sum_{x=1}^{L}2L|N,\ldots,\tau_{x}=i,\ldots,N\rangle -2\sum_{x=1}^{L}(x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle
\end{align}
where we used the fact that 
\begin{equation}\label{eNN-action}
	 e_{NN}^{tot}|\Psi_{0}^{0}\rangle=L|\Psi_{0}^{0}\rangle
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$
\begin{equation}\label{Dij-ref}
	D_{i,j}^{2L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial from the definition of \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ and for all $x\in\{1,\ldots,L\}$ 
\begin{equation}
	D_{i,j}^{2L}||N,\ldots,\tau_{x}=i,\ldots,N\rangle=-2|N,\ldots,\tau_{x}=j,\ldots,N\rangle
\end{equation}
The proof is trivial from \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ 
\begin{equation}\label{GoodRelation}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=-2B_{j}^{2L-1}|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{GoodRelation}:}
\begin{align}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle&= D_{j,i}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-2e_{ji}^{tot}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-4\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=j,\ldots,N\rangle\nonumber
	\\&=
	-2B_{i}|\Psi_{0}^{0}\rangle
\end{align}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $k,j,i\in\{1,\ldots,N-1\}\;:\;k\neq i$
\begin{equation}\label{DijBk-different}
	D_{k,j}^{2L}B_{i}^{L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial following the one of \eqref{GoodRelation}. 
\item For all $ \forall i\in \{1,\ldots,N-1\}$
\begin{equation}\label{Dii-ref}
	D_{i,i}^{2L}\Psi_{0}^{0}\rangle=|\Psi_{0}^{0}\rangle\qquad D_{N,N}^{2L}\Psi_{0}^{0}\rangle=(1+2L)|\Psi_{0}^{0}
\end{equation}
The proof is trivial using \eqref{Dii-charge} and \eqref{DNN-charge}. 
\item $Q_{0}^{2L}$ acts diagonally on the state $|\Psi_{0}^{0}\rangle$
\begin{equation}\label{Diagonal-Q-void}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle=(2L+N)(1+L)|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{Diagonal-Q-void}:}
\begin{align}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle&=\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right)|\Psi_{0}^{0}\rangle\\&=
	\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}\right)|\Psi_{0}^{0}\rangle
	\\&=
	(N-NL-2L+2(N+1)L+2L^{2})|\Psi_{0}^{0}\rangle
\end{align}
where we used the fact that 
\begin{equation}
	\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}|\Psi_{0}^{0}\rangle=0
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\end{itemize}

@@

i.e. $Q_{0}^{2L}B_{i}^{2L-1}$ and $Q_{0}^{2L}B_{j}^{2L-1}$ do commute.

@@

As a consequence of \eqref{veryUsefulSeries} and of \eqref{Two-Relation}, it is easy to prove that for all  $k_{1},\ldots,k_{N-1}\in\mathbb{N}$

@@

	|\Psi_{0}^{0}\rangle
	\\=&\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}!}	\prod_{\ell=1}^{N-1}\left(Q_{0}^{2L}B_{\ell}^{2L-1}\right)^{k_{\ell}}|\Psi_{0}^{0}\rangle

@@

\sum_{t=0}^{\infty}\left\{2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-t}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-t-1}|\Psi_{0}^{0}\rangle
We observe that
	\lim_{\epsilon\to 0}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}\Psi_{0}^{0}=|\Psi_{0}^{0}\rangle
therefore, re-summing the series we obtain
	&\lim_{\epsilon\to 0}\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}
	\lim_{\epsilon\to 0}\sum_{t=0}^{\infty}\left\{Q_{0}^{2L}-2j(D_{1,1}^{2L}+D_{N,N}^{2L})+4j(j-1)\right\}^{-t}\left(\Lambda_{0}+\epsilon\right)^{-t-1}\Psi_{0}^{0}
	\lim_{\epsilon\to 0}\left\{\Lambda_{0}+\epsilon-\Lambda_{0}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle

@@

	&\left\{2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle
	\\=&\left\{2j(2L+2)-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle

>>>>

\textbf{Proof of \eqref{BActionVoid}: } using \eqref{B-charge} we have that 
\begin{align}
	B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=&2 \left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}\sum_{k=1}^{N}e_{kN}^{[a]}e_{jk}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber
	\\=&
	2\left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}e_{NN}^{[a]}e_{jN}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber\\=&
	\sum_{x=1}^{L}2L|N,\ldots,\tau_{x}=i,\ldots,N\rangle -2\sum_{x=1}^{L}(x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle
\end{align}
where we used the fact that 
\begin{equation}\label{eNN-action}
	 e_{NN}^{tot}|\Psi_{0}^{0}\rangle=L|\Psi_{0}^{0}\rangle
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$
\begin{equation}\label{Dij-ref}
	D_{i,j}^{2L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial from the definition of \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ and for all $x\in\{1,\ldots,L\}$ 
\begin{equation}
	D_{i,j}^{2L}||N,\ldots,\tau_{x}=i,\ldots,N\rangle=-2|N,\ldots,\tau_{x}=j,\ldots,N\rangle
\end{equation}
The proof is trivial from \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ 
\begin{equation}\label{GoodRelation}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=-2B_{j}^{2L-1}|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{GoodRelation}:}
\begin{align}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle&= D_{j,i}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-2e_{ji}^{tot}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-4\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=j,\ldots,N\rangle\nonumber
	\\&=
	-2B_{j}|\Psi_{0}^{0}\rangle
\end{align}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $k,j,i\in\{1,\ldots,N-1\}\;:\;k\neq i$
\begin{equation}\label{DijBk-different}
	D_{k,j}^{2L}B_{i}^{L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial following the one of \eqref{GoodRelation}. 
\item For all $ \forall i\in \{1,\ldots,N-1\}$
\begin{equation}\label{Dii-ref}
	D_{i,i}^{2L}\Psi_{0}^{0}\rangle=|\Psi_{0}^{0}\rangle\qquad D_{N,N}^{2L}\Psi_{0}^{0}\rangle=(1+2L)|\Psi_{0}^{0}
\end{equation}
The proof is trivial using \eqref{Dii-charge} and \eqref{DNN-charge}. 
\item $Q_{0}^{2L}$ acts diagonally on the state $|\Psi_{0}^{0}\rangle$
\begin{equation}\label{Diagonal-Q-void}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle=(2L+N)(1+L)|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{Diagonal-Q-void}:}
\begin{align}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle&=\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right)|\Psi_{0}^{0}\rangle\\&=
	\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}\right)|\Psi_{0}^{0}\rangle
	\\&=
	(N-NL-2L+2(N+1)L+2L^{2})|\Psi_{0}^{0}\rangle
\end{align}
where we used the fact that 
\begin{equation}
	\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}|\Psi_{0}^{0}\rangle=0
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\end{itemize}

@@

i.e. $Q_{0}^{2L}B_{i}^{2L-1}$ and $Q_{0}^{2L}B_{j}^{2L-1}$ do commute when acting on $|\Psi_{0}^{0}\rangle$.\\
We further observe that 
\begin{align}\label{Two-Points-m1}
	&\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
	B_{i}^{2L-1}B_{j}^{2L-1}\prod_{j=1}^{2}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2j(D_{11}^{2L}+D_{NN}^{2L})-4j(j-1)\right)^{-1}|\Psi_{0}^{0}\rangle
Indeed, as a consequence of \eqref{veryUsefulSeries}, we have 
	&\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\sum_{n=0}^{\infty}\left\{\left(\Lambda_{0}+\epsilon\right)^{-1}Q_{0}^{2L}\right\}^{n}\left(\Lambda_{0}+\epsilon\right)^{-1}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\sum_{n=0}^{\infty}\left(\Lambda_{0}+\epsilon\right)^{-1-n}(Q_{0}^{2L})^{n}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
We have that, using \eqref{GoodRelation}, \eqref{Dij-ref} and \eqref{Dii-ref},
&(Q_{0}^{2L})^{n}B_{j}^{2L-1}|\Psi_{0}^{0}\rangle=(Q_{0}^{2L})^{n-1}\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)-2\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}^{2L-1}D_{k,i}^{2L}\right\}|\Psi_{0}^{0}\rangle\nonumber
(Q_{0}^{2L})^{n-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle\nonumber
B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)^{n}|\Psi_{0}^{0}\rangle
&\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}B_{i}^{2L-1}\sum_{n=0}^{\infty}\left(\Lambda_{0}+\epsilon\right)^{-1-n}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)^{n}|\Psi_{0}^{0}\rangle\nonumber
\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}B_{i}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)^{-1}|\Psi_{0}^{0}\rangle\nonumber
B_{j}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)^{-1}B_{i}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)^{-1}|\Psi_{0}^{0}\rangle
Using again \eqref{veryUsefulSeries} and applying the same argument we have 
&\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
B_{j}^{2L-1}\sum_{n=0}^{\infty}\left\{\left(\Lambda_{0}+\epsilon\right)^{-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)\right\}^{n}\left(\Lambda_{0}+\epsilon\right)^{-1}B_{i}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)^{-1}|\Psi_{0}^{0}\rangle\nonumber
B_{i}^{2L-1}B_{j}^{2L-1}\prod_{j=1}^{2}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2j(D_{11}^{2L}+D_{NN}^{2L})-4j(j-1)\right)^{-1}|\Psi_{0}^{0}\rangle

@@

As a consequence of \eqref{Two-Points-m1} we have that for all  $k_{1},\ldots,k_{N-1}\in\mathbb{N}$

@@

	|\Psi_{0}^{0}\rangle\nonumber
	\\=&\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}!}	\prod_{\ell=1}^{N-1}\left(Q_{0}^{2L}B_{\ell}^{2L-1}\right)^{k_{\ell}}|\Psi_{0}^{0}\rangle\nonumber

@@

\sum_{t=0}^{\infty}\left\{Q_{0}^{2L}-2j(D_{1,1}^{2L}+D_{N,N}^{2L})+4j(j-1)\right\}^{-t}\left(\Lambda_{0}+\epsilon\right)^{-t-1}|\Psi_{0}^{0}\rangle
Therefore, re-summing the series we obtain
	&\lim_{\epsilon\to 0}\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}\nonumber
	\lim_{\epsilon\to 0}\sum_{t=0}^{\infty}\left\{Q_{0}^{2L}-2j(D_{1,1}^{2L}+D_{N,N}^{2L})+4j(j-1)\right\}^{-t}\left(\Lambda_{0}+\epsilon\right)^{-t-1}|\Psi_{0}^{0}\rangle\nonumber
	\lim_{\epsilon\to 0}\left\{\Lambda_{0}+\epsilon-\Lambda_{0}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle\nonumber

@@

	&\left\{2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle\nonumber
	\\=&\left\{2j(2L+2)-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle\nonumber
